---
title: "Software"
echo: false
---

<link rel="stylesheet" href="https://use.fontawesome.com/releases/v5.12.1/css/all.css" crossorigin="anonymous"> <link rel="stylesheet" href="https://cdn.jsdelivr.net/gh/jpswalsh/academicons@1/css/academicons.min.css">

```{css}
.button {background-color: white;
  color: black;
  border: 1px solid black;}
  
.button:hover {
  background-color: black;
  color: white;
  border: 1px solid black;
}
```

```{r}
bt <- function(link, label, icon){
  bt_ccs <- downloadthis::download_link(
  link = link,
  button_label = label,
  button_type = "default",
  has_icon = TRUE,
  icon = icon,
  self_contained = FALSE,
  button_size = "small",
  class = "button"
  ) 
  shiny::HTML(gsub("\n", "", as.character(bt_ccs)))
}
```

## `dgpsi`

`dgpsi` provides both Python and R implementations for deep and linked Gaussian process emulations. It currently has following features:

* Gaussian process emulations with separable or non-separable squared exponential and Mat&eacute;rn-2.5 kernels.
* Deep Gaussian process emulations with flexible structures including: 
    - multiple layers;
    - multiple GP nodes;
    - separable or non-separable squared exponential and Mat&eacute;rn-2.5 kernels;
    - global input connections;
    - non-Gaussian likelihoods (Poisson, Negative-Binomial, heteroskedastic Gaussian, and Categorical).
* Linked emulations of feed-forward systems of computer models by linking (D)GP emulators of deterministic individual computer models.
* Fast Leave-One-Out (LOO) and Out-Of-Sample (OOS) validations for GP, DGP, and linked (D)GP emulators.
* Multi-core predictions and validations for GP, DGP, and Linked (D)GP emulators.
* Sequential designs for (D)GP emulators and bundles of (D)GP emulators.
* Automatic pruning of DGP emulators, both statically and dynamically.
* Large-scale GP, DGP, and Linked (D)GP emulations.
* Scalable DGP classification using Stochastic Imputation.
* Bayesian optimization.

`r bt("https://mingdeyu.github.io/dgpsi-R/", "Website (R)", "fa fa-globe")` `r bt("https://github.com/mingdeyu/dgpsi-R", "Github (R)", "fab fa-github")` `r bt("https://github.com/mingdeyu/DGP", "Github (Python)", "fab fa-github")` `r bt("https://cloud.r-project.org/web/packages/dgpsi/index.html", "CRAN", "fab fa-r-project")` `r bt("https://anaconda.org/conda-forge/dgpsi", "Conda", "fab fa-python")`

<!--
```{r embed-xaringan, echo=FALSE}
xaringanExtra::embed_xaringan(url = "tutorial.html", ratio = "4:3")
```
-->
